Dependency in Refinement Logics

### 2015-10-17 doc/paper.tex
notation switch; wordsmithing

\newcommand\ThenStateTrans[5]{%
  \InputMode{#2}\dashv\InputMode{#3}%
  \hookrightarrow_\InputMode{#1}%
  \OutputMode{#4}\dashv\OutputMode{#5}%
}

@@

This is clearly unsatisfactory, since it breaks the natural flow of proof
development, whereby multiple goals may be refined simultaneously without
committing in advance to a particular solution. However, a more palatable
refinement rule that allows $\IsTrue{A}$ to be demonstrated by refinement is
simply not expressible in \ModLCF, since the sense of the second subgoal cannot
be expressed except by referring to the synthesis of the first subgoal.

>>>>

\newcommand\ThenStateTrans[5]{%
  \InputMode{#2}\dashv\InputMode{#3}%
  \Downarrow_\InputMode{#1}%
  \OutputMode{#4}\dashv\OutputMode{#5}%
}

@@

This is clearly unsatisfactory, since it breaks the natural flow of proof
development, whereby multiple goals may be refined simultaneously without
committing in advance to a particular solution. However, a more palatable
rule that allows $\IsTrue{A}$ to be demonstrated by refinement is
simply not expressible in \ModLCF, since the sense of the second subgoal cannot
be expressed except by referring to the synthesis of the first subgoal.
